### 2018-02-20 Writing/disparity_review.tex
Contributions?

\noindent {\normalsize \sc Thomas Guillerme$^1$$^,$$^*$, Natalie Cooper$^2$, Stephen Brusatte$^3$, Katie Davis$^4$, Andrew Jackson$^5$, Sylvain Gerber$^6$, Anjali Goswami$^2$, Kevin Healy$^7$, Melanie Hopkins$^8$, Graeme Lloyd$^9$, Joseph O'Reilly$^{10}$, Abi Pate$^{10}$, Emilie Rayfield$^{10}$, Erin Saupe$^{11}$, Emma Sherratt$^{12}$, Graham Slater$^{13}$, Gavin H Thomas$^{14}$ and Philip Donoghue$^{10}$}\\

\noindent {\small \it 
$^1$School of Biological Sciences, University of Queensland, St. Lucia, Queensland, Australia.; $^2$NHM; $^{10}$Bristol}
\end{center}
\medskip
\noindent{*\bf Corresponding author.} \textit{guillert@tcd.ie}\\  
\vspace{1in}

@@

>>>>

\noindent {\normalsize \sc Thomas Guillerme$^{1,*,+}$, Natalie Cooper$^{2,+}$, Stephen Brusatte$^3$, Katie Davis$^4$, Andrew Jackson$^5$, Sylvain Gerber$^6$, Anjali Goswami$^2$, Kevin Healy$^7$, Melanie Hopkins$^8$, Graeme Lloyd$^9$, Joseph O'Reilly$^{10}$, Abi Pate$^{10}$, Emilie Rayfield$^{10}$, Erin Saupe$^{11}$, Emma Sherratt$^{12}$, Graham Slater$^{13}$, Gavin H Thomas$^{14}$ and Philip Donoghue$^{10,+}$}\\

\noindent {\small \it 
$^1$School of Biological Sciences, University of Queensland, St. Lucia, Queensland, Australia.; $^2$NHM; $^{10}$Bristol}
\end{center}
\medskip
\noindent{+ These authors contributed equally to the manuscript.}
\noindent{*\bf Corresponding author.} \textit{guillert@tcd.ie}\\  
\vspace{1in}

@@

\section{Authors contribution}
TG, NC and PD proposed the idea of this review. TG, NC, SB, KD, AJ, SG, AG, KH, MH, GL, JOR, AP, ER, ES, ES, GS, GHT and PD wrote the manuscript,
